\documentclass[green]{avatar}
\begin{document}
\name{\gHerbalism{}}

\cenquote{"Sick of tea? That's like being sick of breathing!"}{-- Uncle Iroh}
\cenquote{"Hmmm.... Delectable tea, or deadly poison?}{-- Uncle Iroh}

\section{Introduction}
You can create herbal products by combining various herbs to produce a result. Herbal products are represented by item packets and you might not know the effects of what you are about to use before you apply it. 

Herbal products come in 6 variations, tea, tincture, salve, decoction, bath, and incense. Each has a different method of application, see the Rules and Scenario for everything but tea, which is below. There are constraints on the number of active effects you can have from herbal sources, again see the Rules and Scenario for everything but tea, which is below.

Herbal products are created by blending items together. This will generally be ingredients labeled \textbf{Ingredient} but there may be exceptions. You can also use herbal products in new herbal blends. You will be able to view the result before committing to make a blend so feel free to experiment.

\section{Herbal Blends}

In order to make an herbal blend, you may use up to six items. In order to attempt to blend, you must have all the items you are attempting to use on your person at the time of the mix, you may not attempt to use items you have already used or that you saw once. 

To attempt to make a blend, use the /blend-herbs command on our discord bot, Hawky. The command accepts up to 6 integers which are the item numbers of the items you are trying to use. The bot will respond with a message that shows the rules text the blend would have if you were to make it, the label for the envelope in the box room that holds the packets for the particular blend, and the number of packets you should take. You do not have to actually make the blend, you can experiment with different combinations of ingredients without using them before you settle on something to produce. (If you just want to test out how to input the command, you can use the item number 0000 which is not a real item.) The order of the ingredients is not mechanically relevant as the bot sorts them into descending order before processing.

When you do decide to actually make a blend, destroy the items you used. Then go to the box room and locate the relevant envelope. Cut out the appropriate number of packets and staple them. If the number of packets in the envelope is running low, please inform the GMs. If you are unsure of the proper way to staple the packets, please ask a GM, NPC, or the Game Mommy for help.

There is a deterministic set of rules for which blend results from a particular set of ingredients. Some characters may start knowing some of these rules. Some of this information may be discovered on items or signs in game. We have tried to design the set of rules such that they can be discovered in game by somebody who is dedicated to figuring them out. The flavor text on the ingredients might give you hints about the properties of that ingredient.

\section{Applying Teas}

There are two steps to applying tea. The first is to brew it, and the second is to serve it. You may only mechanically benefit from tea brewed by a particular person once per day. You may only consume tea for mechanical effect four times per day. You may drink as much tea as you like.

When purchasing tea from a tea shop, you must immediately drink the tea and may not take the tea elsewhere unless you know otherwise (exceptions will generally be stated on the sign).

\subsection{Brewing Tea}

In order to brew tea, you must have an item card labeled "Tea Blend". Because the amount of time to brew and the temperature at which to brew at can be very particular, you may only brew a particular tea blend if you have mixed that blend yourself in the past, though the blend may be obtained from other sources. 

In order to brew tea, you must do the following steps in order:

\TODO{Steps to brewing tea}

\begin{itemz}
    \item Boil water using a...
\end{itemz}

\subsection{Serving Tea}

You may only serve tea that you brewed within the last 10 minutes. Only a total of 5 people may mechanically benefit from drinking a particular blend at one time. The persons serving can be one of the five people. Others may participate in drinking tea without gaining the benefits.

\TODO{Flavor steps to serving tea}

In order to brew tea, you must do the following steps in order:

\begin{itemz}
    \item Gather up to...
\end{itemz}

\end{document}