
% ===== COMMON =====

\NEW{Item}{\iAirBooze}{
  \s\MYname     {Ingredient: Meadow Mead}
  \s\MYnumber   {5400}
  \s\MYtext     {\textit{A pale green-gold honey wine with floral notes}

\textbf{alcohol}
}
}

\NEW{Item}{\iAirIncense}{
  \s\MYname     {Ingredient: Greenveil}
  \s\MYnumber   {5408}
  \s\MYtext     {\textit{Pale green incense that burns with a fresh, floral scent.}


}
}

\NEW{Item}{\iAirLightBasicBane}{
  \s\MYname     {Ingredient: Mourner's Shade}
  \s\MYnumber   {5462}
  \s\MYtext     {\textit{Dull green-indigo leaves.}


}
}

\NEW{Item}{\iAirLightBasicBoon}{
  \s\MYname     {Ingredient: Clearheart Fern}
  \s\MYnumber   {5461}
  \s\MYtext     {\textit{A green fern with indigo spores}


}
}

\NEW{Item}{\iAirSalt}{
  \s\MYname     {Ingredient: Meadow Salt}
  \s\MYnumber   {5407}
  \s\MYtext     {\textit{Pale green salt harvested from highland mineral springs.}

\textbf{salt}
}
}

\NEW{Item}{\iAirSoundBasicBane}{
  \s\MYname     {Ingredient: Bittervetch}
  \s\MYnumber   {5452}
  \s\MYtext     {\textit{A stringy green-blue plant with a sour taste.}


}
}

\NEW{Item}{\iAirSoundBasicBoon}{
  \s\MYname     {Ingredient: Kindspeech Clover}
  \s\MYnumber   {5451}
  \s\MYtext     {\textit{A green clover with blue-tinged leaves.}


}
}

\NEW{Item}{\iAirThoughtBasicBane}{
  \s\MYname     {Ingredient: Griefcling}
  \s\MYnumber   {5472}
  \s\MYtext     {\textit{A tangled green-violet creeper.}


}
}

\NEW{Item}{\iAirThoughtBasicBoon}{
  \s\MYname     {Ingredient: Letting-Go Leaf}
  \s\MYnumber   {5471}
  \s\MYtext     {\textit{A heart-shaped green leaf with violet edges.}


}
}

\NEW{Item}{\iEarthAirBasicBane}{
  \s\MYname     {Ingredient: Coldroot}
  \s\MYnumber   {5142}
  \s\MYtext     {\textit{A pale root with a bitter, metallic taste. The bark is red on the outside but green when you cut into it.}


}
}

\NEW{Item}{\iEarthAirBasicBoon}{
  \s\MYname     {Ingredient: Meadowfoot}
  \s\MYnumber   {5141}
  \s\MYtext     {\textit{A low-growing plant with red stems and green leaves.}


}
}

\NEW{Item}{\iEarthBooze}{
  \s\MYname     {Ingredient: Redroot Whiskey}
  \s\MYnumber   {5100}
  \s\MYtext     {\textit{A dark reddish-brown spirit distilled from root vegetables.}

\textbf{alcohol}
}
}

\NEW{Item}{\iEarthFireBasicBane}{
  \s\MYname     {Ingredient: Cinder Ash}
  \s\MYnumber   {5132}
  \s\MYtext     {\textit{Gray-yellow powder with flecks of red. Made from burned deadwood.}


}
}

\NEW{Item}{\iEarthFireBasicBoon}{
  \s\MYname     {Ingredient: Hearthstone Herb}
  \s\MYnumber   {5131}
  \s\MYtext     {\textit{A red-yellow leafy plant that grows near hot springs.}


}
}

\NEW{Item}{\iEarthIncense}{
  \s\MYname     {Ingredient: Rootsmoke}
  \s\MYnumber   {5108}
  \s\MYtext     {\textit{Dark red resin that burns with a heavy, earthy scent.}


}
}

\NEW{Item}{\iEarthLightBasicBane}{
  \s\MYname     {Ingredient: Blindstone Powder}
  \s\MYnumber   {5162}
  \s\MYtext     {\textit{Gritty indigo-red dust that stings the eyes.}


}
}

\NEW{Item}{\iEarthLightBasicBoon}{
  \s\MYname     {Ingredient: Deepseeing Root}
  \s\MYnumber   {5161}
  \s\MYtext     {\textit{A reddish root with indigo veins.}


}
}

\NEW{Item}{\iEarthSalt}{
  \s\MYname     {Ingredient: Redite}
  \s\MYnumber   {5107}
  \s\MYtext     {\textit{Coarse red-brown salt mined from deep caverns.}

\textbf{salt}
}
}

\NEW{Item}{\iEarthSoundBasicBane}{
  \s\MYname     {Ingredient: Choking Dust}
  \s\MYnumber   {5152}
  \s\MYtext     {\textit{Fine reddish-blue powder made from the ground claw of a seagull-squirrel}


}
}

\NEW{Item}{\iEarthSoundBasicBoon}{
  \s\MYname     {Ingredient: Groundsong Moss}
  \s\MYnumber   {5151}
  \s\MYtext     {\textit{Red-tinged blue moss that grows on old standing stones.}


}
}

\NEW{Item}{\iEarthThoughtBasicBane}{
  \s\MYname     {Ingredient: Obsession Root}
  \s\MYnumber   {5172}
  \s\MYtext     {\textit{A tough, dull red-violet root.}


}
}

\NEW{Item}{\iEarthThoughtBasicBoon}{
  \s\MYname     {Ingredient: Anchorbloom}
  \s\MYnumber   {5171}
  \s\MYtext     {\textit{A red-stemmed flower with pale violet petals}


}
}

\NEW{Item}{\iEarthWaterBasicBane}{
  \s\MYname     {Ingredient: Swamprot}
  \s\MYnumber   {5122}
  \s\MYtext     {\textit{A slimy reddish orange root collected from stagnant water.}


}
}

\NEW{Item}{\iEarthWaterBasicBoon}{
  \s\MYname     {Ingredient: Marshroot}
  \s\MYnumber   {5121}
  \s\MYtext     {\textit{A sturdy red-orange tuber found in wetlands.}


}
}

\NEW{Item}{\iFireAirBasicBane}{
  \s\MYname     {Ingredient: Ashenvine}
  \s\MYnumber   {5342}
  \s\MYtext     {\textit{A brittle yellow-gray vine.}


}
}

\NEW{Item}{\iFireAirBasicBoon}{
  \s\MYname     {Ingredient: Boldvine}
  \s\MYnumber   {5341}
  \s\MYtext     {\textit{A yellow-green climbing plant.}


}
}

\NEW{Item}{\iFireBooze}{
  \s\MYname     {Ingredient: Goldgrain Vodka}
  \s\MYnumber   {5300}
  \s\MYtext     {\textit{A clear spirit with a faint yellow tint and sharp heat. Drinkers report feeling bolder after a glass.}

\textbf{alcohol}
}
}

\NEW{Item}{\iFireIncense}{
  \s\MYname     {Ingredient: Goldspice Cone}
  \s\MYnumber   {5308}
  \s\MYtext     {\textit{Bright yellow incense cones with a sharp, peppery smoke.}


}
}

\NEW{Item}{\iFireLightBasicBane}{
  \s\MYname     {Ingredient: Dimflame Powder}
  \s\MYnumber   {5362}
  \s\MYtext     {\textit{Dull yellow-indigo powder.}


}
}

\NEW{Item}{\iFireLightBasicBoon}{
  \s\MYname     {Ingredient: Clearflame Herb}
  \s\MYnumber   {5361}
  \s\MYtext     {\textit{Bright yellow leaves with an indigo sheen.}


}
}

\NEW{Item}{\iFireSalt}{
  \s\MYname     {Ingredient: Sulphur Flake}
  \s\MYnumber   {5307}
  \s\MYtext     {\textit{Bright yellow crystalline salt with a sharp bite.}

\textbf{salt}
}
}

\NEW{Item}{\iFireSoundBasicBane}{
  \s\MYname     {Ingredient: Hesitant Herb}
  \s\MYnumber   {5352}
  \s\MYtext     {\textit{Pale yellow-blue leaves that crumble easily.}


}
}

\NEW{Item}{\iFireSoundBasicBoon}{
  \s\MYname     {Ingredient: Orator's Seed}
  \s\MYnumber   {5351}
  \s\MYtext     {\textit{Small yellow-blue seeds with a peppery taste.}


}
}

\NEW{Item}{\iFireThoughtBasicBane}{
  \s\MYname     {Ingredient: Grasping Weed}
  \s\MYnumber   {5372}
  \s\MYtext     {\textit{A tough yellow-violet weed. Saps confidence while creating mental fixation.}


}
}

\NEW{Item}{\iFireThoughtBasicBoon}{
  \s\MYname     {Ingredient: Purposebloom}
  \s\MYnumber   {5371}
  \s\MYtext     {\textit{A yellow flower with violet-tipped petals.}


}
}

\NEW{Item}{\iLightBooze}{
  \s\MYname     {Ingredient: Midnight Port}
  \s\MYnumber   {5600}
  \s\MYtext     {\textit{A deep indigo fortified wine. Sipped slowly, it seems to sharpen perception even as it relaxes.}

\textbf{alcohol}
}
}

\NEW{Item}{\iLightIncense}{
  \s\MYname     {Ingredient: Seer's Coil}
  \s\MYnumber   {5608}
  \s\MYtext     {\textit{Deep indigo incense spirals that burn slowly.}


}
}

\NEW{Item}{\iLightSalt}{
  \s\MYname     {Ingredient: Twilight Salt}
  \s\MYnumber   {5607}
  \s\MYtext     {\textit{Dusky indigo salt from remote mountain deposits.}

\textbf{salt}
}
}

\NEW{Item}{\iLightThoughtBasicBane}{
  \s\MYname     {Ingredient: Veilmoss}
  \s\MYnumber   {5672}
  \s\MYtext     {\textit{Gray-violet moss with sublte indigo that grows in dark places.}


}
}

\NEW{Item}{\iLightThoughtBasicBoon}{
  \s\MYname     {Ingredient: Wisdomcap}
  \s\MYnumber   {5671}
  \s\MYtext     {\textit{A small mushroom, indigo cap with violet gills.}


}
}

\NEW{Item}{\iNeutralBooze}{
  \s\MYname     {Ingredient: Grain Spirits}
  \s\MYnumber   {5004}
  \s\MYtext     {\textit{Clear alcohol distilled from common grain.}

\textbf{alcohol}
}
}

\NEW{Item}{\iNeutralIncense}{
  \s\MYname     {Ingredient: Scentsap}
  \s\MYnumber   {5002}
  \s\MYtext     {\textit{A simple dried tree sap that burns with a mild, woody smoke}


}
}

\NEW{Item}{\iNeutralSalt}{
  \s\MYname     {Ingredient: Ground Salt}
  \s\MYnumber   {5001}
  \s\MYtext     {\textit{Plain white salt harvested from coastal flats.}

\textbf{salt}
}
}

\NEW{Item}{\iNeutralTea}{
  \s\MYname     {Ingredient: Dried Leaf Blend}
  \s\MYnumber   {5003}
  \s\MYtext     {\textit{A mixture of common dried leaves with a mild, earthy flavor.}


}
}

\NEW{Item}{\iPureAirBaneBottom}{
  \s\MYname     {Ingredient: Coldleaf}
  \s\MYnumber   {5402}
  \s\MYtext     {\textit{A pale green leaf that feels cool to the touch.}


}
}

\NEW{Item}{\iPureAirBoonBottom}{
  \s\MYname     {Ingredient: Gentlegreen Sprig}
  \s\MYnumber   {5401}
  \s\MYtext     {\textit{A common green herb with a mild, grassy taste.}


}
}

\NEW{Item}{\iPureEarthBaneBottom}{
  \s\MYname     {Ingredient: Worry Weed}
  \s\MYnumber   {5102}
  \s\MYtext     {\textit{A stringy, crimson root, often found in neglected fields.}


}
}

\NEW{Item}{\iPureEarthBoonBottom}{
  \s\MYname     {Ingredient: Dustwalker's Burr}
  \s\MYnumber   {5101}
  \s\MYtext     {\textit{A common reddish seed pod that often clings to travelers' clothes.}


}
}

\NEW{Item}{\iPureFireBaneBottom}{
  \s\MYname     {Ingredient: Flickerweed}
  \s\MYnumber   {5302}
  \s\MYtext     {\textit{A faded yellow grass that wilts quickly after picking.}


}
}

\NEW{Item}{\iPureFireBoonBottom}{
  \s\MYname     {Ingredient: Ember Seed}
  \s\MYnumber   {5301}
  \s\MYtext     {\textit{Tiny yellow seeds that leave a warm tingle on the tongue.}


}
}

\NEW{Item}{\iPureLightBaneBottom}{
  \s\MYname     {Ingredient: Dimleaf}
  \s\MYnumber   {5602}
  \s\MYtext     {\textit{A grayish-indigo leaf that crumbles easily.}


}
}

\NEW{Item}{\iPureLightBoonBottom}{
  \s\MYname     {Ingredient: Midnight Berries}
  \s\MYnumber   {5601}
  \s\MYtext     {\textit{Small indigo berries with a tart taste.}


}
}

\NEW{Item}{\iPureSoundBaneBottom}{
  \s\MYname     {Ingredient: Hushing Moss}
  \s\MYnumber   {5502}
  \s\MYtext     {\textit{Dull blue moss that grows in quiet places.}


}
}

\NEW{Item}{\iPureSoundBoonBottom}{
  \s\MYname     {Ingredient: Clearwater Mint}
  \s\MYnumber   {5501}
  \s\MYtext     {\textit{A pale blue mint leaf with a cooling sensation when chewed}


}
}

\NEW{Item}{\iPureThoughtBaneBottom}{
  \s\MYname     {Ingredient: Clinging Ivy}
  \s\MYnumber   {5702}
  \s\MYtext     {\textit{A dark violet vine that's nearly impossible to remove.}


}
}

\NEW{Item}{\iPureThoughtBoonBottom}{
  \s\MYname     {Ingredient: Stillmind Petal}
  \s\MYnumber   {5701}
  \s\MYtext     {\textit{A pale violet lichen found on old timber.}


}
}

\NEW{Item}{\iPureWaterBaneBottom}{
  \s\MYname     {Ingredient: Joyless Husk}
  \s\MYnumber   {5202}
  \s\MYtext     {\textit{A faded orange shell from a flower seed.}


}
}

\NEW{Item}{\iPureWaterBoonBottom}{
  \s\MYname     {Ingredient: Mellowseed}
  \s\MYnumber   {5201}
  \s\MYtext     {\textit{Small orange seeds with a mild, nutty taste.}


}
}

\NEW{Item}{\iSoundBooze}{
  \s\MYname     {Ingredient: Bluecoast Rum}
  \s\MYnumber   {5500}
  \s\MYtext     {\textit{A smooth blue-tinged rum from coastal distilleries. Loosens the tongue and encourages frank conversation.}

\textbf{alcohol}
}
}

\NEW{Item}{\iSoundIncense}{
  \s\MYname     {Ingredient: Blue Smoke Stick}
  \s\MYnumber   {5508}
  \s\MYtext     {\textit{Slender blue incense with a clean, almost metallic scent.}


}
}

\NEW{Item}{\iSoundLightBasicBane}{
  \s\MYname     {Ingredient: Mutterwort}
  \s\MYnumber   {5562}
  \s\MYtext     {\textit{Blue-gray leaves with an indigo tinge.}


}
}

\NEW{Item}{\iSoundLightBasicBoon}{
  \s\MYname     {Ingredient: Truthseer's Mint}
  \s\MYnumber   {5561}
  \s\MYtext     {\textit{A blue-indigo mint with a sharp, clean taste.}


}
}

\NEW{Item}{\iSoundSalt}{
  \s\MYname     {Ingredient: Blue Brine Crystal}
  \s\MYnumber   {5507}
  \s\MYtext     {\textit{Faint blue salt crystals from deep ocean evaporation.}

\textbf{salt}
}
}

\NEW{Item}{\iSoundThoughtBasicBane}{
  \s\MYname     {Ingredient: Babbling Moss}
  \s\MYnumber   {5572}
  \s\MYtext     {\textit{Dull blue-violet moss.}


}
}

\NEW{Item}{\iSoundThoughtBasicBoon}{
  \s\MYname     {Ingredient: Stillvoice Petal}
  \s\MYnumber   {5571}
  \s\MYtext     {\textit{Blue petals with violet centers.}


}
}

\NEW{Item}{\iThoughtBooze}{
  \s\MYname     {Ingredient: Monastery Wine}
  \s\MYnumber   {5700}
  \s\MYtext     {\textit{A pale violet wine made by contemplative orders.}

\textbf{alcohol}
}
}

\NEW{Item}{\iThoughtIncense}{
  \s\MYname     {Ingredient: Templetop Resin}
  \s\MYnumber   {5708}
  \s\MYtext     {\textit{Pale violet resin that burns with a sublte scent.}


}
}

\NEW{Item}{\iThoughtSalt}{
  \s\MYname     {Ingredient: Peakstone Salt}
  \s\MYnumber   {5707}
  \s\MYtext     {\textit{Violet-tinged salt from the highest elevations.}

\textbf{salt}
}
}

\NEW{Item}{\iWaterAirBasicBane}{
  \s\MYname     {Ingredient: Numbvine}
  \s\MYnumber   {5242}
  \s\MYtext     {\textit{A limp orange-green vine.}


}
}

\NEW{Item}{\iWaterAirBasicBoon}{
  \s\MYname     {Ingredient: Sweetbrier}
  \s\MYnumber   {5241}
  \s\MYtext     {\textit{A thorny plant with orange flowers and green leaves.}


}
}

\NEW{Item}{\iWaterBooze}{
  \s\MYname     {Ingredient: Orchard Brandy}
  \s\MYnumber   {5200}
  \s\MYtext     {\textit{A smooth orange-amber brandy made from stone fruits.}

\textbf{alcohol}
}
}

\NEW{Item}{\iWaterFireBasicBane}{
  \s\MYname     {Ingredient: Sourember}
  \s\MYnumber   {5232}
  \s\MYtext     {\textit{A shriveled orange-yellow fruit with an acrid taste.}


}
}

\NEW{Item}{\iWaterFireBasicBoon}{
  \s\MYname     {Ingredient: Sunfruit Rind}
  \s\MYnumber   {5231}
  \s\MYtext     {\textit{Dried peel from a citrus fruit, orange fading to yellow.}


}
}

\NEW{Item}{\iWaterIncense}{
  \s\MYname     {Ingredient: Amber Coil}
  \s\MYnumber   {5208}
  \s\MYtext     {\textit{Orange-brown incense sticks that smell of warm honey and fruit.}


}
}

\NEW{Item}{\iWaterLightBasicBane}{
  \s\MYname     {Ingredient: Fogfruit}
  \s\MYnumber   {5262}
  \s\MYtext     {\textit{A soft orange-indigo fruit that tastes of nothing.}


}
}

\NEW{Item}{\iWaterLightBasicBoon}{
  \s\MYname     {Ingredient: Dawnpetal}
  \s\MYnumber   {5261}
  \s\MYtext     {\textit{Orange petals edged with indigo, it is said to be most beautiful in the morning dew.}


}
}

\NEW{Item}{\iWaterSalt}{
  \s\MYname     {Ingredient: Sunset Salt}
  \s\MYnumber   {5207}
  \s\MYtext     {\textit{Fine orange-tinted salt from warm coastal pools.}

\textbf{salt}
}
}

\NEW{Item}{\iWaterSoundBasicBane}{
  \s\MYname     {Ingredient: Siltweed}
  \s\MYnumber   {5252}
  \s\MYtext     {\textit{Muddy orange-blue strands pulled from riverbeds.}


}
}

\NEW{Item}{\iWaterSoundBasicBoon}{
  \s\MYname     {Ingredient: Honeyvoice Leaf}
  \s\MYnumber   {5251}
  \s\MYtext     {\textit{A waxy orange-blue leaf with a faintly sweet taste.}


}
}

\NEW{Item}{\iWaterThoughtBasicBane}{
  \s\MYname     {Ingredient: Clinging Sap}
  \s\MYnumber   {5272}
  \s\MYtext     {\textit{Sticky orange-violet resin that won't wash off.}


}
}

\NEW{Item}{\iWaterThoughtBasicBoon}{
  \s\MYname     {Ingredient: Blissbloom}
  \s\MYnumber   {5271}
  \s\MYtext     {\textit{A small orange blossom with violet stamens.}


}
}


% ===== UNCOMMON =====

\NEW{Item}{\iAirEarthBane}{
  \s\MYname     {Ingredient: Grieving Instability}
  \s\MYnumber   {5416}
  \s\MYtext     {\textit{A wilted green-gray herb with red-tinged roots.}


}
}

\NEW{Item}{\iAirEarthBoon}{
  \s\MYname     {Ingredient: Rooted Heart Vine}
  \s\MYnumber   {5415}
  \s\MYtext     {\textit{A deep green vine with red berries.}


}
}

\NEW{Item}{\iAirFireBane}{
  \s\MYname     {Ingredient: Cold-Hearted Doubt}
  \s\MYnumber   {5436}
  \s\MYtext     {\textit{Pale green-yellow leaves that feel cold to the touch.}


}
}

\NEW{Item}{\iAirFireBoon}{
  \s\MYname     {Ingredient: Loving Courage}
  \s\MYnumber   {5435}
  \s\MYtext     {\textit{Vivid green leaves with yellow edges.}


}
}

\NEW{Item}{\iAirLightBane}{
  \s\MYname     {Ingredient: Blind Sorrow}
  \s\MYnumber   {5466}
  \s\MYtext     {\textit{Dull green-indigo leaves that crumble at a touch.}


}
}

\NEW{Item}{\iAirLightBoon}{
  \s\MYname     {Ingredient: Clearseeing Heart}
  \s\MYnumber   {5465}
  \s\MYtext     {\textit{Green heart-shaped leaves with indigo undersides.}


}
}

\NEW{Item}{\iAirSoundBane}{
  \s\MYname     {Ingredient: Silent Grief}
  \s\MYnumber   {5456}
  \s\MYtext     {\textit{A withered green-blue vine.}


}
}

\NEW{Item}{\iAirSoundBoon}{
  \s\MYname     {Ingredient: Trueheart Clover}
  \s\MYnumber   {5455}
  \s\MYtext     {\textit{A large green clover with blue-tinged stems.}


}
}

\NEW{Item}{\iAirThoughtBane}{
  \s\MYname     {Ingredient: Grieving Obsession}
  \s\MYnumber   {5476}
  \s\MYtext     {\textit{A tangled green-violet creeper.}


}
}

\NEW{Item}{\iAirThoughtBoon}{
  \s\MYname     {Ingredient: Unattached Love}
  \s\MYnumber   {5475}
  \s\MYtext     {\textit{A green flower with violet stamens.}


}
}

\NEW{Item}{\iAirWaterBane}{
  \s\MYname     {Ingredient: Loveless Numbness}
  \s\MYnumber   {5426}
  \s\MYtext     {\textit{A dull green-orange leaf that tastes of sorrow.}


}
}

\NEW{Item}{\iAirWaterBoon}{
  \s\MYname     {Ingredient: Compassion Fruit}
  \s\MYnumber   {5425}
  \s\MYtext     {\textit{A green-skinned fruit with orange flesh.}


}
}

\NEW{Item}{\iEarthAirBane}{
  \s\MYname     {Ingredient: Terror Vine}
  \s\MYnumber   {5146}
  \s\MYtext     {\textit{A gray-red creeper with withered green leaves.}


}
}

\NEW{Item}{\iEarthAirBoon}{
  \s\MYname     {Ingredient: Steadfast Heartleaf}
  \s\MYnumber   {5145}
  \s\MYtext     {\textit{A red-stemmed plant with broad green leaves.}


}
}

\NEW{Item}{\iEarthFireBane}{
  \s\MYname     {Ingredient: Scorched Root}
  \s\MYnumber   {5136}
  \s\MYtext     {\textit{A blackened root with red and yellow streaks, dug from fire-damaged soil.}


}
}

\NEW{Item}{\iEarthFireBoon}{
  \s\MYname     {Ingredient: Foundite Root}
  \s\MYnumber   {5135}
  \s\MYtext     {\textit{A heavy red-yellow root that grows near volcanic soil.}


}
}

\NEW{Item}{\iEarthLightBane}{
  \s\MYname     {Ingredient: Blind Panic Root}
  \s\MYnumber   {5166}
  \s\MYtext     {\textit{A twisted red-gray root with indigo spots.}


}
}

\NEW{Item}{\iEarthLightBoon}{
  \s\MYname     {Ingredient: Cavern Crystal Herb}
  \s\MYnumber   {5165}
  \s\MYtext     {\textit{A red-veined plant with indigo flowers that grows in dim caves.}


}
}

\NEW{Item}{\iEarthSoundBane}{
  \s\MYname     {Ingredient: Silencing Dread}
  \s\MYnumber   {5156}
  \s\MYtext     {\textit{A crumbling red-gray root with blue mold.}


}
}

\NEW{Item}{\iEarthSoundBoon}{
  \s\MYname     {Ingredient: Bedrock Tongue}
  \s\MYnumber   {5155}
  \s\MYtext     {\textit{A tough red root with blue-tinged bark}


}
}

\NEW{Item}{\iEarthThoughtBane}{
  \s\MYname     {Ingredient: Obsessive Terror}
  \s\MYnumber   {5176}
  \s\MYtext     {\textit{A gnarled red-violet root that's hard to uproot.}


}
}

\NEW{Item}{\iEarthThoughtBoon}{
  \s\MYname     {Ingredient: Mountain Anchor}
  \s\MYnumber   {5175}
  \s\MYtext     {\textit{A tough red root with pale violet nodules, found at high elevations.}


}
}

\NEW{Item}{\iEarthWaterBane}{
  \s\MYname     {Ingredient: Bog Rot}
  \s\MYnumber   {5126}
  \s\MYtext     {\textit{A spongy red-orange fungus pulled from stagnant marshes.}


}
}

\NEW{Item}{\iEarthWaterBoon}{
  \s\MYname     {Ingredient: Deepmarsh Tuber}
  \s\MYnumber   {5125}
  \s\MYtext     {\textit{A dense red tuber with orange flesh, found in fertile wetlands.}


}
}

\NEW{Item}{\iFireAirBane}{
  \s\MYname     {Ingredient: Heartless Doubt}
  \s\MYnumber   {5346}
  \s\MYtext     {\textit{Withered yellow-green leaves.}


}
}

\NEW{Item}{\iFireAirBoon}{
  \s\MYname     {Ingredient: Courage Bloom}
  \s\MYnumber   {5345}
  \s\MYtext     {\textit{A vivid yellow flower with green leaves shaped like hearts.}


}
}

\NEW{Item}{\iFireEarthBane}{
  \s\MYname     {Ingredient: Ash Tuber}
  \s\MYnumber   {5316}
  \s\MYtext     {\textit{A mealy yellow tuber coated in reddish volcanic ash.}


}
}

\NEW{Item}{\iFireEarthBoon}{
  \s\MYname     {Ingredient: Brazier's Foundation}
  \s\MYnumber   {5315}
  \s\MYtext     {\textit{A bright yellow root with red outer bark.}


}
}

\NEW{Item}{\iFireLightBane}{
  \s\MYname     {Ingredient: Blind Hesitation}
  \s\MYnumber   {5366}
  \s\MYtext     {\textit{A dull yellow-indigo herb.}


}
}

\NEW{Item}{\iFireLightBoon}{
  \s\MYname     {Ingredient: Clearpath Pepper}
  \s\MYnumber   {5365}
  \s\MYtext     {\textit{An intensely yellow pepper with indigo seeds.}


}
}

\NEW{Item}{\iFireSoundBane}{
  \s\MYname     {Ingredient: Hesitant Tongue}
  \s\MYnumber   {5356}
  \s\MYtext     {\textit{Pale yellow-blue powder that numbs the mouth.}


}
}

\NEW{Item}{\iFireSoundBoon}{
  \s\MYname     {Ingredient: Commander's Herb}
  \s\MYnumber   {5355}
  \s\MYtext     {\textit{Bright yellow leaves with blue veins.}


}
}

\NEW{Item}{\iFireThoughtBane}{
  \s\MYname     {Ingredient: Grasping Failure}
  \s\MYnumber   {5376}
  \s\MYtext     {\textit{A tough yellow-violet weed that spreads aggressively.}


}
}

\NEW{Item}{\iFireThoughtBoon}{
  \s\MYname     {Ingredient: Focused Flame Seed}
  \s\MYnumber   {5375}
  \s\MYtext     {\textit{Small yellow seeds with violet hulls.}


}
}

\NEW{Item}{\iFireWaterBane}{
  \s\MYname     {Ingredient: Shameful Numbness}
  \s\MYnumber   {5326}
  \s\MYtext     {\textit{A bitter yellow-orange extract.}


}
}

\NEW{Item}{\iFireWaterBoon}{
  \s\MYname     {Ingredient: Golden Citrus}
  \s\MYnumber   {5325}
  \s\MYtext     {\textit{A yellow fruit with orange flesh and sharp, warming juice.}


}
}

\NEW{Item}{\iLightAirBane}{
  \s\MYname     {Ingredient: Loveless Fog}
  \s\MYnumber   {5646}
  \s\MYtext     {\textit{A wilted indigo-green herb.}


}
}

\NEW{Item}{\iLightAirBoon}{
  \s\MYname     {Ingredient: Compassionate Sight}
  \s\MYnumber   {5645}
  \s\MYtext     {\textit{An indigo flower with green leaves.}


}
}

\NEW{Item}{\iLightEarthBane}{
  \s\MYname     {Ingredient: Unstable Illusion}
  \s\MYnumber   {5616}
  \s\MYtext     {\textit{A pale indigo-gray mushroom with red spores.}


}
}

\NEW{Item}{\iLightEarthBoon}{
  \s\MYname     {Ingredient: Seer's Anchor}
  \s\MYnumber   {5615}
  \s\MYtext     {\textit{An indigo-flowered plant with red roots.}


}
}

\NEW{Item}{\iLightFireBane}{
  \s\MYname     {Ingredient: Doubting Blindness}
  \s\MYnumber   {5636}
  \s\MYtext     {\textit{Faded indigo-yellow leaves.}


}
}

\NEW{Item}{\iLightFireBoon}{
  \s\MYname     {Ingredient: Resolute Vision}
  \s\MYnumber   {5635}
  \s\MYtext     {\textit{Indigo leaves with yellow edges.}


}
}

\NEW{Item}{\iLightSoundBane}{
  \s\MYname     {Ingredient: Deceiving Veil}
  \s\MYnumber   {5656}
  \s\MYtext     {\textit{Murky indigo-blue fungus.}


}
}

\NEW{Item}{\iLightSoundBoon}{
  \s\MYname     {Ingredient: Truthseeker's Eye}
  \s\MYnumber   {5655}
  \s\MYtext     {\textit{Indigo petals with blue stamens.}


}
}

\NEW{Item}{\iLightThoughtBane}{
  \s\MYname     {Ingredient: Obsessive Illusion}
  \s\MYnumber   {5676}
  \s\MYtext     {\textit{A dark indigo-violet mushroom.}


}
}

\NEW{Item}{\iLightThoughtBoon}{
  \s\MYname     {Ingredient: Detached Clarity}
  \s\MYnumber   {5675}
  \s\MYtext     {\textit{An indigo mushroom with violet gills.}


}
}

\NEW{Item}{\iLightWaterBane}{
  \s\MYname     {Ingredient: Joyless Confusion}
  \s\MYnumber   {5626}
  \s\MYtext     {\textit{Dull indigo-orange berries.}


}
}

\NEW{Item}{\iLightWaterBoon}{
  \s\MYname     {Ingredient: Joyful Clarity}
  \s\MYnumber   {5625}
  \s\MYtext     {\textit{Indigo berries with orange flesh.}


}
}

\NEW{Item}{\iSoundAirBane}{
  \s\MYname     {Ingredient: Loveless Silence}
  \s\MYnumber   {5546}
  \s\MYtext     {\textit{A withered blue-green herb.}


}
}

\NEW{Item}{\iSoundAirBoon}{
  \s\MYname     {Ingredient: Kindword Blossom}
  \s\MYnumber   {5545}
  \s\MYtext     {\textit{A blue flower with green-tinged petals.}


}
}

\NEW{Item}{\iSoundEarthBane}{
  \s\MYname     {Ingredient: Unstable Lies}
  \s\MYnumber   {5516}
  \s\MYtext     {\textit{A twisted blue-gray root with red mold.}


}
}

\NEW{Item}{\iSoundEarthBoon}{
  \s\MYname     {Ingredient: Grounded Voice}
  \s\MYnumber   {5515}
  \s\MYtext     {\textit{A blue-barked root with red inner flesh.}


}
}

\NEW{Item}{\iSoundFireBane}{
  \s\MYname     {Ingredient: Weak-Voiced Doubt}
  \s\MYnumber   {5536}
  \s\MYtext     {\textit{Pale blue-yellow leaves with a bitter taste.}


}
}

\NEW{Item}{\iSoundFireBoon}{
  \s\MYname     {Ingredient: Bold Speaker's Leaf}
  \s\MYnumber   {5535}
  \s\MYtext     {\textit{Bright blue leaves with yellow veins.}


}
}

\NEW{Item}{\iSoundLightBane}{
  \s\MYname     {Ingredient: Blind Deception}
  \s\MYnumber   {5566}
  \s\MYtext     {\textit{Murky blue-indigo moss.}


}
}

\NEW{Item}{\iSoundLightBoon}{
  \s\MYname     {Ingredient: Clearspeech Crystal}
  \s\MYnumber   {5565}
  \s\MYtext     {\textit{Blue crystalline herb with indigo tips.}


}
}

\NEW{Item}{\iSoundThoughtBane}{
  \s\MYname     {Ingredient: Obsessive Lies}
  \s\MYnumber   {5576}
  \s\MYtext     {\textit{A tough blue-violet weed.}


}
}

\NEW{Item}{\iSoundThoughtBoon}{
  \s\MYname     {Ingredient: Stillvoice Bloom}
  \s\MYnumber   {5575}
  \s\MYtext     {\textit{A blue flower with violet center.}


}
}

\NEW{Item}{\iSoundWaterBane}{
  \s\MYname     {Ingredient: Joyless Deception}
  \s\MYnumber   {5526}
  \s\MYtext     {\textit{A slimy blue-orange weed.}


}
}

\NEW{Item}{\iSoundWaterBoon}{
  \s\MYname     {Ingredient: Joyful Honesty}
  \s\MYnumber   {5525}
  \s\MYtext     {\textit{Blue berries with orange juice.}


}
}

\NEW{Item}{\iThoughtAirBane}{
  \s\MYname     {Ingredient: Loveless Grasping}
  \s\MYnumber   {5746}
  \s\MYtext     {\textit{A tangled violet-green vine.}


}
}

\NEW{Item}{\iThoughtAirBoon}{
  \s\MYname     {Ingredient: Loving Detachment}
  \s\MYnumber   {5745}
  \s\MYtext     {\textit{A violet flower with green heart-shaped leaves.}


}
}

\NEW{Item}{\iThoughtEarthBane}{
  \s\MYname     {Ingredient: Unstable Fixation}
  \s\MYnumber   {5716}
  \s\MYtext     {\textit{A gnarled violet-gray root with red streaks.}


}
}

\NEW{Item}{\iThoughtEarthBoon}{
  \s\MYname     {Ingredient: Grounded Peace}
  \s\MYnumber   {5715}
  \s\MYtext     {\textit{A violet flower with red-brown stems.}


}
}

\NEW{Item}{\iThoughtFireBane}{
  \s\MYname     {Ingredient: Doubting Attachment}
  \s\MYnumber   {5736}
  \s\MYtext     {\textit{Tough violet-yellow stems.}


}
}

\NEW{Item}{\iThoughtFireBoon}{
  \s\MYname     {Ingredient: Purposeful Stillness}
  \s\MYnumber   {5735}
  \s\MYtext     {\textit{Violet leaves with yellow veins}


}
}

\NEW{Item}{\iThoughtLightBane}{
  \s\MYname     {Ingredient: Blind Attachment}
  \s\MYnumber   {5766}
  \s\MYtext     {\textit{A dark violet-indigo fungus.}


}
}

\NEW{Item}{\iThoughtLightBoon}{
  \s\MYname     {Ingredient: Clear Emptiness}
  \s\MYnumber   {5765}
  \s\MYtext     {\textit{A pale violet mushroom with indigo cap.}


}
}

\NEW{Item}{\iThoughtSoundBane}{
  \s\MYname     {Ingredient: Silent Obsession}
  \s\MYnumber   {5756}
  \s\MYtext     {\textit{Dull violet-blue moss.}


}
}

\NEW{Item}{\iThoughtSoundBoon}{
  \s\MYname     {Ingredient: Honest Stillness}
  \s\MYnumber   {5755}
  \s\MYtext     {\textit{Violet petals with blue stems.}


}
}

\NEW{Item}{\iThoughtWaterBane}{
  \s\MYname     {Ingredient: Joyless Obsession}
  \s\MYnumber   {5276}
  \s\MYtext     {\textit{Shriveled violet-orange berries.}


}
}

\NEW{Item}{\iThoughtWaterBoon}{
  \s\MYname     {Ingredient: Contented Release}
  \s\MYnumber   {5275}
  \s\MYtext     {\textit{Pale violet berries with orange juice.}


}
}

\NEW{Item}{\iWaterAirBane}{
  \s\MYname     {Ingredient: Shameful Silence}
  \s\MYnumber   {5246}
  \s\MYtext     {\textit{A slimy orange-blue weed from polluted water.}


}
}

\NEW{Item}{\iWaterAirBoon}{
  \s\MYname     {Ingredient: Kindwater Blossom}
  \s\MYnumber   {5245}
  \s\MYtext     {\textit{An orange flower with green-tinged petals that blooms near streams.}


}
}

\NEW{Item}{\iWaterEarthBane}{
  \s\MYname     {Ingredient: Sinkhole Fruit}
  \s\MYnumber   {5216}
  \s\MYtext     {\textit{A mushy orange fruit with a gritty red core, found near eroded riverbanks.}


}
}

\NEW{Item}{\iWaterEarthBoon}{
  \s\MYname     {Ingredient: Riverbed Orange}
  \s\MYnumber   {5215}
  \s\MYtext     {\textit{A bright orange fruit with red-brown rind from riverside orchards.}


}
}

\NEW{Item}{\iWaterFireBane}{
  \s\MYname     {Ingredient: Joyless Ember}
  \s\MYnumber   {5236}
  \s\MYtext     {\textit{A dull orange-yellow paste that tastes of nothing.}


}
}

\NEW{Item}{\iWaterFireBoon}{
  \s\MYname     {Ingredient: Sunpool Nectar}
  \s\MYnumber   {5235}
  \s\MYtext     {\textit{Thick orange-yellow syrup collected from tropical flowers.}


}
}

\NEW{Item}{\iWaterLightBane}{
  \s\MYname     {Ingredient: Fogbound Guilt}
  \s\MYnumber   {5266}
  \s\MYtext     {\textit{A pale orange-indigo berry that tastes of regret.}


}
}

\NEW{Item}{\iWaterLightBoon}{
  \s\MYname     {Ingredient: Clearwater Peach}
  \s\MYnumber   {5265}
  \s\MYtext     {\textit{An orange fruit with indigo-tinged skin from mountain springs.}


}
}

\NEW{Item}{\iWaterSoundBane}{
  \s\MYname     {Ingredient: Drowned Singer}
  \s\MYnumber   {5256}
  \s\MYtext     {\textit{A waterlogged orange-blue reed pulled from murky ponds.}


}
}

\NEW{Item}{\iWaterSoundBoon}{
  \s\MYname     {Ingredient: Flowing Voice Fruit}
  \s\MYnumber   {5255}
  \s\MYtext     {\textit{A juicy orange fruit with blue seeds.}


}
}

\NEW{Item}{\iWaterThoughtBane}{
  \s\MYname     {Ingredient: Clinging Regret}
  \s\MYnumber   {5726}
  \s\MYtext     {\textit{Sticky orange-violet sap that won't wash clean.}


}
}

\NEW{Item}{\iWaterThoughtBoon}{
  \s\MYname     {Ingredient: Releasing Apricot}
  \s\MYnumber   {5725}
  \s\MYtext     {\textit{A soft orange fruit with violet flesh.}


}
}


% ===== RARE =====

\NEW{Item}{\iAirHarm}{
  \s\MYname     {Ingredient: Heartbreak Leaf}
  \s\MYnumber   {5494}
  \s\MYtext     {\textit{A crumpled green leaf with brittle, brown-edged veins.}


}
}

\NEW{Item}{\iAirHeal}{
  \s\MYname     {Ingredient: Heartmender's Green}
  \s\MYnumber   {5493}
  \s\MYtext     {\textit{A vibrant green leaf}


}
}

\NEW{Item}{\iAntiThoughtBooze}{
  \s\MYname     {Ingredient: Grasping Grain}
  \s\MYnumber   {5706}
  \s\MYtext     {\textit{A harsh violet-black spirit with a bitter aftertaste.}

\textbf{alcohol}
}
}

\NEW{Item}{\iBigHarm}{
  \s\MYname     {Ingredient: Whiteish Red Flower}
  \s\MYnumber   {5999}
  \s\MYtext     {\textit{This seems either very tasty, or very poisonous... You aren't sure which.}


}
}

\NEW{Item}{\iBigHeal}{
  \s\MYname     {Ingredient: Redish White Flower}
  \s\MYnumber   {5998}
  \s\MYtext     {\textit{This seems either very tasty, or very poisonous... You aren't sure which.}


}
}

\NEW{Item}{\iEarthHarm}{
  \s\MYname     {Ingredient: Maka'ole Berry}
  \s\MYnumber   {5194}
  \s\MYtext     {\textit{A shiny reddish berry.}


}
}

\NEW{Item}{\iEarthHeal}{
  \s\MYname     {Ingredient: Bacui Berry}
  \s\MYnumber   {5193}
  \s\MYtext     {\textit{A shiny reddish berry.}


}
}

\NEW{Item}{\iFireHarm}{
  \s\MYname     {Ingredient: Brimstone Seed}
  \s\MYnumber   {5394}
  \s\MYtext     {\textit{Small yellow seeds with a harsh, acrid taste.}


}
}

\NEW{Item}{\iLightHarm}{
  \s\MYname     {Ingredient: Blindcap}
  \s\MYnumber   {5694}
  \s\MYtext     {\textit{A pale indigo mushroom that grows in total darkness.}


}
}

\NEW{Item}{\iLightHeal}{
  \s\MYname     {Ingredient: Indigo Eye}
  \s\MYnumber   {5693}
  \s\MYtext     {\textit{A round indigo fruit with a pale center resembling a pupil.}


}
}

\NEW{Item}{\iPureAirBaneMiddle}{
  \s\MYname     {Ingredient: Bittervine}
  \s\MYnumber   {5404}
  \s\MYtext     {\textit{A dull green creeper with a sour smell.}


}
}

\NEW{Item}{\iPureAirBaneTop}{
  \s\MYname     {Ingredient: Griefhollow Thorn}
  \s\MYnumber   {5406}
  \s\MYtext     {\textit{A pale green thorn that is said to draw no blood when it pricks.}


}
}

\NEW{Item}{\iPureAirBoonMiddle}{
  \s\MYname     {Ingredient: Kindly Clover}
  \s\MYnumber   {5403}
  \s\MYtext     {\textit{A four-leafed clover of vivid green}


}
}

\NEW{Item}{\iPureAirBoonTop}{
  \s\MYname     {Ingredient: Heartleaf Wreath}
  \s\MYnumber   {5405}
  \s\MYtext     {\textit{Broad, deep green leaves shaped like hearts.}


}
}

\NEW{Item}{\iPureEarthBaneMiddle}{
  \s\MYname     {Ingredient: Uprooted Pale}
  \s\MYnumber   {5104}
  \s\MYtext     {\textit{A sickly red root with no smell.}


}
}

\NEW{Item}{\iPureEarthBaneTop}{
  \s\MYname     {Ingredient: Quakeleaf}
  \s\MYnumber   {5106}
  \s\MYtext     {\textit{A brittle, reddish leaf that crumbles at a touch.}


}
}

\NEW{Item}{\iPureEarthBoonMiddle}{
  \s\MYname     {Ingredient: Clinging Moss}
  \s\MYnumber   {5103}
  \s\MYtext     {\textit{Rust-colored moss typically scraped from stone foundations.}


}
}

\NEW{Item}{\iPureEarthBoonTop}{
  \s\MYname     {Ingredient: Ironroot Heart}
  \s\MYnumber   {5105}
  \s\MYtext     {\textit{A dense, red-veined tuber, generally dug from beneath old-growth trees.}


}
}

\NEW{Item}{\iPureFireBaneMiddle}{
  \s\MYname     {Ingredient: PureFireBaneMiddle}
  \s\MYnumber   {5304}
  \s\MYtext     {\textit{A withered yellow-gray vine.}


}
}

\NEW{Item}{\iPureFireBaneTop}{
  \s\MYname     {Ingredient: Ashmouth Root}
  \s\MYnumber   {5306}
  \s\MYtext     {\textit{A pale, chalky yellow root that tastes of nothing.}


}
}

\NEW{Item}{\iPureFireBoonMiddle}{
  \s\MYname     {Ingredient: Goldbark Shavings}
  \s\MYnumber   {5303}
  \s\MYtext     {\textit{Curled strips of bright yellow bark with a sharp, spicy scent.}


}
}

\NEW{Item}{\iPureFireBoonTop}{
  \s\MYname     {Ingredient: Brazier Pepper}
  \s\MYnumber   {5305}
  \s\MYtext     {\textit{An intensely yellow pepper that burns going down.}


}
}

\NEW{Item}{\iPureLightBaneMiddle}{
  \s\MYname     {Ingredient: Fogwort}
  \s\MYnumber   {5604}
  \s\MYtext     {\textit{A faded indigo herb with an unpleasant smell.}


}
}

\NEW{Item}{\iPureLightBaneTop}{
  \s\MYname     {Ingredient: Veilcap Mushroom}
  \s\MYnumber   {5606}
  \s\MYtext     {\textit{A pale indigo mushroom that grows in complete darkness.}


}
}

\NEW{Item}{\iPureLightBoonMiddle}{
  \s\MYname     {Ingredient: Duskpetal}
  \s\MYnumber   {5603}
  \s\MYtext     {\textit{Deep indigo petals with that faintly shimmer in the setting sunlight}


}
}

\NEW{Item}{\iPureLightBoonTop}{
  \s\MYname     {Ingredient: Third-Eye Orchid}
  \s\MYnumber   {5605}
  \s\MYtext     {\textit{A rare indigo flower that blooms only in shade.}


}
}

\NEW{Item}{\iPureSoundBaneMiddle}{
  \s\MYname     {Ingredient: Murky Amanita}
  \s\MYnumber   {5504}
  \s\MYtext     {\textit{A murky blue-gray herb that numbs the tongue.}


}
}

\NEW{Item}{\iPureSoundBaneTop}{
  \s\MYname     {Ingredient: Liar's Root}
  \s\MYnumber   {5506}
  \s\MYtext     {\textit{A twisted blue-black root with a bitter aftertaste.}


}
}

\NEW{Item}{\iPureSoundBoonMiddle}{
  \s\MYname     {Ingredient: Truestem}
  \s\MYnumber   {5503}
  \s\MYtext     {\textit{A bright blue stalk with a clean, mineral taste.}


}
}

\NEW{Item}{\iPureSoundBoonTop}{
  \s\MYname     {Ingredient: Bellflower Tongue}
  \s\MYnumber   {5505}
  \s\MYtext     {\textit{A deep blue flower that hums faintly in a breeze.}


}
}

\NEW{Item}{\iPureThoughtBaneMiddle}{
  \s\MYname     {Ingredient: Grasping Fern}
  \s\MYnumber   {5704}
  \s\MYtext     {\textit{A dull violet fern with curling fronds.}


}
}

\NEW{Item}{\iPureThoughtBoonMiddle}{
  \s\MYname     {Ingredient: Driftwood Lichen}
  \s\MYnumber   {5703}
  \s\MYtext     {\textit{Soft violet petals with almost no scent}


}
}

\NEW{Item}{\iPureThoughtBoonTop}{
  \s\MYname     {Ingredient: Crownbloom}
  \s\MYnumber   {5705}
  \s\MYtext     {\textit{A striking violet flower that grows at high altitudes.}


}
}

\NEW{Item}{\iPureWaterBaneMiddle}{
  \s\MYname     {Ingredient: Hollow Rind}
  \s\MYnumber   {5204}
  \s\MYtext     {\textit{A desiccated orange peel, dry and bitter.}


}
}

\NEW{Item}{\iPureWaterBaneTop}{
  \s\MYname     {Ingredient: Sourstone Shavings}
  \s\MYnumber   {5206}
  \s\MYtext     {\textit{Flakes of a pale orange mineral with a sharp, unpleasant scent.}


}
}

\NEW{Item}{\iPureWaterBoonMiddle}{
  \s\MYname     {Ingredient: Sunstone Petal}
  \s\MYnumber   {5203}
  \s\MYtext     {\textit{Bright orange petals that smell faintly of honey.}


}
}

\NEW{Item}{\iPureWaterBoonTop}{
  \s\MYname     {Ingredient: Amberfruit Pulp}
  \s\MYnumber   {5205}
  \s\MYtext     {\textit{A sticky orange paste collected from ripe fruit}


}
}

\NEW{Item}{\iSoundHarm}{
  \s\MYname     {Ingredient: Chokeweed}
  \s\MYnumber   {5594}
  \s\MYtext     {\textit{A stringy blue plant that leaves a scratchy feeling in the throat.}


}
}

\NEW{Item}{\iSoundHeal}{
  \s\MYname     {Ingredient: Songbird Seed}
  \s\MYnumber   {5593}
  \s\MYtext     {\textit{Small blue seeds said to be favored by the sweetest-singing birds.}


}
}

\NEW{Item}{\iThoughtHarm}{
  \s\MYname     {Ingredient: Obsession}
  \s\MYnumber   {5794}
  \s\MYtext     {\textit{A fine violet powder that clings to skin and clothing.}


}
}

\NEW{Item}{\iThoughtHeal}{
  \s\MYname     {Ingredient: Violet Cap}
  \s\MYnumber   {5793}
  \s\MYtext     {\textit{A delicate violet mushroom with a calming, earthy flavor.}


}
}

\NEW{Item}{\iWaterHarm}{
  \s\MYname     {Ingredient: Weeping Rind}
  \s\MYnumber   {5294}
  \s\MYtext     {\textit{A soft orange peel that oozes a sour-smelling liquid.}


}
}

\NEW{Item}{\iWaterHeal}{
  \s\MYname     {Ingredient: Sacui Berry}
  \s\MYnumber   {5293}
  \s\MYtext     {\textit{A plump orange berry with a sweet juice.}


}
}


% ===== SPIRIT WORLD =====

\NEW{Item}{\iSpiritAirBane}{
  \s\MYname     {Ingredient: Hollow Heart}
  \s\MYnumber   {5484}
  \s\MYtext     {\textit{A translucent gray-green flower that feels empty when held.}


}
}

\NEW{Item}{\iSpiritAirBoon}{
  \s\MYname     {Ingredient: Spiritheart Blossom}
  \s\MYnumber   {5483}
  \s\MYtext     {\textit{A softly glowing green flower that drifts without wind.}


}
}

\NEW{Item}{\iSpiritEarthBane}{
  \s\MYname     {Ingredient: Unmooring Root}
  \s\MYnumber   {5184}
  \s\MYtext     {\textit{A gray-red root that feels like nothing when held.}


}
}

\NEW{Item}{\iSpiritEarthBoon}{
  \s\MYname     {Ingredient: Ghostroot}
  \s\MYnumber   {5183}
  \s\MYtext     {\textit{A translucent red root}


}
}

\NEW{Item}{\iSpiritFireBane}{
  \s\MYname     {Ingredient: Haunt's Despair}
  \s\MYnumber   {5384}
  \s\MYtext     {\textit{A pale yellow pod that gives off cold instead of warmth.}


}
}

\NEW{Item}{\iSpiritFireBoon}{
  \s\MYname     {Ingredient: Willwisp Pepper}
  \s\MYnumber   {5383}
  \s\MYtext     {\textit{A faintly luminous yellow pod}


}
}

\NEW{Item}{\iSpiritLightBane}{
  \s\MYname     {Ingredient: Veilshroud}
  \s\MYnumber   {5684}
  \s\MYtext     {\textit{A dark indigo fungus that absorbs light.}


}
}

\NEW{Item}{\iSpiritLightBoon}{
  \s\MYname     {Ingredient: Veilpiercer}
  \s\MYnumber   {5683}
  \s\MYtext     {\textit{An indigo flower that glows brighter in darkness.}


}
}

\NEW{Item}{\iSpiritSoundBane}{
  \s\MYname     {Ingredient: Silencing Mist}
  \s\MYnumber   {5584}
  \s\MYtext     {\textit{A blue-gray vapor that clings to the throat.}


}
}

\NEW{Item}{\iSpiritSoundBoon}{
  \s\MYname     {Ingredient: Echoing Blue}
  \s\MYnumber   {5583}
  \s\MYtext     {\textit{A pale blue herb that hums faintly when touched.}


}
}

\NEW{Item}{\iSpiritThoughtBane}{
  \s\MYname     {Ingredient: Binding Moss}
  \s\MYnumber   {5784}
  \s\MYtext     {\textit{A dull violet moss that clings stubbornly to anything it touches.}


}
}

\NEW{Item}{\iSpiritThoughtBoon}{
  \s\MYname     {Ingredient: Passing Bloom}
  \s\MYnumber   {5783}
  \s\MYtext     {\textit{A delicate violet flower that seems to fade in and out of existence.}


}
}

\NEW{Item}{\iSpiritWaterHerbBane}{
  \s\MYname     {Ingredient: Regret Lily}
  \s\MYnumber   {5284}
  \s\MYtext     {\textit{A dull orange flower that wilts when observed.}


}
}

\NEW{Item}{\iSpiritWaterHerbBoon}{
  \s\MYname     {Ingredient: Phantom Lily}
  \s\MYnumber   {5283}
  \s\MYtext     {\textit{A glowing orange flower}


}
}


% ===== SPECIAL =====

\NEW{Item}{\iSpiritSlimeAir}{
  \s\MYname     {Ingredient: Verdent Ecoplasmic Gel}
  \s\MYnumber   {5849}
  \s\MYtext     {\textit{A soft, green-hued gel}

\textbf{alcohol}
}
}

\NEW{Item}{\iSpiritSlimeEarth}{
  \s\MYname     {Ingredient: Red Ectoplasmic Gel}
  \s\MYnumber   {5819}
  \s\MYtext     {\textit{A thick, red-tinged gel}

\textbf{alcohol}
}
}

\NEW{Item}{\iSpiritSlimeFire}{
  \s\MYname     {Ingredient: Golden Ectoplasmic Gel}
  \s\MYnumber   {5839}
  \s\MYtext     {\textit{A faintly warm, yellow-tinged gel}

\textbf{alcohol}
}
}

\NEW{Item}{\iSpiritSlimeLight}{
  \s\MYname     {Ingredient: Indigo Ectoplasmic Gel}
  \s\MYnumber   {5869}
  \s\MYtext     {\textit{A shimmering, indigo-hued gel}

\textbf{alcohol}
}
}

\NEW{Item}{\iSpiritSlimeNeutral}{
  \s\MYname     {Ingredient: Ectoplasmic Residue}
  \s\MYnumber   {5809}
  \s\MYtext     {\textit{A colorless, slightly luminous gel}


}
}

\NEW{Item}{\iSpiritSlimeSound}{
  \s\MYname     {Ingredient: Azure Ectoplasmic Gel}
  \s\MYnumber   {5859}
  \s\MYtext     {\textit{A cool, blue-tinged gel}

\textbf{alcohol}
}
}

\NEW{Item}{\iSpiritSlimeThought}{
  \s\MYname     {Ingredient: Violet Ectoplasmic Gel}
  \s\MYnumber   {5879}
  \s\MYtext     {\textit{A pale, violet-tinged}

\textbf{alcohol}
}
}

\NEW{Item}{\iSpiritSlimeWater}{
  \s\MYname     {Ingredient: Amber Ectoplasmic Gel}
  \s\MYnumber   {5829}
  \s\MYtext     {\textit{A warm, orange-hued gel}

\textbf{alcohol}
}
}


% ===== RERE =====

\NEW{Item}{\iFireHeal}{
  \s\MYname     {Ingredient: Goldenrod Bulb}
  \s\MYnumber   {5393}
  \s\MYtext     {\textit{A bright yellow bulb with a warm, peppery taste.}


}
}
